### 2021-11-22 input/proposal.tex
meow

\begin{theorem}[\label{theo:efb}\underline{F}orwarding of \underline{B}est (FB)
  $\implies\eventually$CP] Assuming reliable communication links
  ($s_{pq}(m) \iff \eventually r_{qp}(m)$), \processes eventually
  reach consistent partitioning if each \process delivers the message
  notifying its shortest path weight to a source among its set of
  \underline{r}eceived messages $R_p$ ($(m = \min R_p) \implies
  d_p(m)$), and forwards the message notifying its shortest path
  weight to a source $s$ among its set of \underline{d}elivered
  messages $D_p$ ($(m = \min D_p) \implies f_p(m)$).
\end{theorem}

@@

  \noindent Such a source $s$ forwards $\alpha_{s}$ to its neighbors.
  Since communication links are reliable, neighboring \processes
  eventually receive such a notification $\forall \langle s, q \rangle
  \in E \iff \eventually r_q(\alpha_{s})$. Most importantly,
  whatever the order of received messages, every \process $q$ in this
  neighborhood such that there exists no closer source $s'$ than the
  received one $s$, delivers it, since $|\Pi_{sq}| < |\Pi_{s'q}|$.

@@

Algorithm~\ref{algo:add} shows the instructions that implement
forwarding of best to reach consistent partitioning when
\begin{inparaenum}[(i)]
\item weights are scalar values,
\item \processes only add new partitions to the system,
\item and \processes never crash nor leave the system.
\end{inparaenum} \TODO{Disambiguator and comparison with $\alpha < A$.}
\TODO{Why not towards parent?}
Figure~\ref{fig:add} illustrates its behavior on a system comprising 4
\processes $a$, $b$, $c$, and $d$. \Process~$a$ and \Process~$d$
become the sources of their partition. They \NAMEB a notification
\underline{a}dd message: $\alpha_a^0$ and $\alpha_d^0$. They
initialize their own state with the lowest possible bound $0$ (see
Line~\ref{line:lowestbound}), and send a message to each of their
neighbors by accumulating the corresponding edge weight (see
Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, \Process~$b$
receives $\alpha_{d}^{1}$. Since it improves its own partition
distance, it keeps it and forwards it to its neighbors. In
Figure~\ref{fig:addD}, \Process~$b$ discards $\alpha_{a}^{2}$, for it
does not improve its partition distance. \Processes $c$ and $d$ will
never acknowledge that Source~$a$ exists. Ultimately, \processes
discard last transiting messages. Despite the obvious lack of traffic
optimization, the system reaches consistent partitioning.

>>>>

\begin{theorem}[\label{theo:efb}\underline{F}orwarding of \underline{B}est (FB)
    $\implies\eventually$CP]
  %
  Assuming reliable communication links ($s_{pq}(m) \iff \eventually
  r_{qp}(m)$), \processes eventually reach consistent partitioning if
  each \process delivers and forwards its best message among
  \underline{r}eceived messages $R_p$, \ie the message $\alpha_s^d$
  with the smallest distance $d$ to the source $s$ ($(\alpha_s^d = \min R_p)
  \implies (d_p(\alpha_s^d) \wedge f_p(\TODO{\alpha_s^d}))$).
\end{theorem}

@@

  \noindent Such a source $s$ forwards $\alpha_{s}$ to its neighbors.
  Since communication links are reliable, neighboring \processes
  eventually receive such a notification $\forall \langle s, q \rangle
  \in E \iff \eventually r_q(\alpha_{s}^{w_{pq}})$. Most importantly,
  whatever the order of received messages, every \process $q$ in this
  neighborhood such that there exists no closer source $s'$ than the
  received one $s$, delivers it, since $|\Pi_{sq}| < |\Pi_{s'q}|$.

@@

Algorithm~\ref{algo:add} shows the instructions that implement
forwarding of best to reach consistent partitioning when
\begin{inparaenum}[(i)]
\item weights are scalar values piggybacked in messages and
  accumulated over forwardings,
\item \processes only add new partitions to the system,
\item and \processes never join, crash nor leave the system.
\end{inparaenum}
For the sake of simplicity, a \process does not forward a notification
to its sender (Line~\ref{line:accumulator}).  Figure~\ref{fig:add}
illustrates its behavior on a system comprising 4 \processes $a$, $b$,
$c$, and $d$. \Process~$a$ and \Process~$d$ become the sources of
their partition.  They \NAMEB a notification \underline{a}dd message:
$\alpha_a^0$ and $\alpha_d^0$. They initialize their own state with
the lowest possible bound $0$ (see Line~\ref{line:lowestbound}), and
send a message to each of their neighbors by accumulating the
corresponding edge weight (see Line~\ref{line:accumulator}). In
Figure~\ref{fig:addC}, \Process~$b$ receives $\alpha_{d}^{1}$. Since
it improves its own partition distance, it keeps it and forwards it to
its neighbors. In Figure~\ref{fig:addD}, \Process~$b$ discards
$\alpha_{a}^{2}$, for it does not improve its partition
distance. \Processes $c$ and $d$ will never acknowledge that
Source~$a$ exists. Ultimately, \processes discard last transiting
messages. Despite the obvious lack of traffic optimization, the system
reaches consistent partitioning.
